---
title: "SiqueiraCampos_proj2"
author: "Marco Siqueira Campos"
date: "9 de outubro de 2016"
output: html_document
---


DATA 607  
MSDA CUNY  

PROJECT 2  
ASSIGNMENT WK5 
Tidying and Transforming Data  

github [link](https://github.com/MarcoSCampos/DATA607_proj2)

EXERCISE 3
Citizenship by region

Proposal: Jose Zuniga

Source: Tips for Simplifying Crosstab Query Statements, Rob Gravelle, Database Journal, 2010.


load library
```{r load_library, warning=FALSE, message=FALSE}
library(tidyr)
library(dplyr)
```

read and check csv file 
```{r read_file}
df_td<-read.table("~/proj2_1.csv",sep=",",stringsAsFactors = FALSE)
df_td
```

Cleaning

Remove rows and columns
```{r remove_rows}
df_td<-df_td[-11,]
df_td$V7<-NULL
```

Set columns names and remove line 1
```{r set_names}
colnames(df_td)[1:6]<-df_td[1,1:6]
df_td<-df_td[-1,]
```

Gather the data
```{r gather}
df_td2<-gather(df_td,"region","citizenship",2:6)
```

Change data type
```{r change}
df_td2['region']<-lapply(df_td2['region'], factor)
df_td2['citizenship']<-lapply(df_td2['citizenship'], as.numeric)
```

**The data is tidy!**
```{r tidy}
df_td2
```

Time to begin to analyse
```{r analy}
df_td2 %>% 
        group_by(Month)%>%
        mutate(row=1:n())%>%
        spread(Month,citizenship)%>%
        select(-row)%>%
        select(region, April, May, June, July, August, September, October, November, December)
```        

We can analyse same month, like August, for several regions
```{r month}
df_td2%>%
    filter(Month=="August")
```
