---
title: "SiqueiraCampos_proj2"
author: "Marco Siqueira Campos"
date: "9 de outubro de 2016"
output: html_document
---

DATA 607  
MSDA CUNY  

PROJECT 2  
ASSIGNMENT WK5     
Tidying and Transforming Data  

github [link](https://github.com/MarcoSCampos/DATA607_proj2)

EXERCISE 1
Gender income inequality

Proposal: Ahsanul Choudhury

From: Census USA
Source: http://www.census.gov/population/age/data/files/2012/2012gender_table17.csv

load library

```{r load_library, warning=FALSE, message=FALSE}
library(tidyr)
library(dplyr)
```

read and check csv file 

```{r read_file}
df<-read.table("~/2012gender_table17.csv",sep=",",stringsAsFactors = FALSE)
head(df, n=25)
```

Cleaning

Remove rows and create a new variable "gender".

```{r remove_rows}
df<-df[-c(1:5,46:53),]
df$v24[30:40]<-"Female"        
df$v24[17:27]<-"Male"
df$v24[4:14]<-"Both sexes"
df<-df[-c(3,15,16,28,29),]        
```

New columns name

```{r column_name}
colnames(df)[1]<-"year"
colnames(df)[24]<-"gender"
colnames(df)[2:11]<-c("totaln","totalp","below5kn","below5kp","from05kto9.9kn","from05kto9.9kp","from10kto14.9kn","from10kto14.9kp","from15kto19.9Kn","from15kto19.9Kp") 
colnames(df)[12:23]<-c("from20kto24.9n","from20kto24.9p","from25kto34.9Kn","from25kto34.9Kp","from35kto49.9kn","from35kto49.9kp","from50kto74.9kn","from50kto74.9kp","from75kto99.9kn","from75kto99.9kp","more100kn","more100kp")
```

Remove rows
```{r remove_rows2}
df<-df[-c(1,2),]
```

Change year variable to improve the search

```{r change_year}
df$year[c(1,12,23)]<-"15_to_17years"
df$year[c(2,13,24)]<-"18_to_24years"
df$year[c(3,14,25)]<-"25_to_29years"
df$year[c(4,15,26)]<-"30_to_34years"
df$year[c(5,16,27)]<-"35_to_39years"
df$year[c(6,17,28)]<-"40_to_44years"
df$year[c(7,18,29)]<-"45_to_49years"
df$year[c(8,19,30)]<-"50_to_54years"
df$year[c(9,20,31)]<-"55_to_59years"
df$year[c(10,21,32)]<-"60_to_64years"
df$year[c(11,22,33)]<-"65_years_and_over" 
```
Melt columns (Number e Percent)

```{r melt_columns}
u<-df%>%
        unite(totaln,totalp,col="total",sep="/")%>%
        unite(below5kn,below5kp,col="below5k",sep="/")%>%
        unite(from05kto9.9kn,from05kto9.9kp,col="from05kto9,9k",sep="/")%>%
        unite(from10kto14.9kn,from10kto14.9kp,col="from10kto14,9k",sep="/")%>%
        unite(from15kto19.9Kn,from15kto19.9Kp,col="from15kto19,9K",sep="/")%>%
        unite(from20kto24.9n,from20kto24.9p,col="from20kto24,9",sep="/")%>%
        unite(from25kto34.9Kn,from25kto34.9Kp,col="from25kto34,9K",sep="/")%>%
        unite(from35kto49.9kn,from35kto49.9kp,col="from35kto49,9k",sep="/")%>%
        unite(from50kto74.9kn,from50kto74.9kp,col="from50kto74,9k",sep="/")%>%
        unite(from75kto99.9kn,from75kto99.9kp,col="from75kto99,9k",sep="/")%>%
        unite(more100kn,more100kp,col="more100k",sep="/")
```        
        

Gather the data, moving to several columns to one column

```{r gather}
g<-gather(u,"Earnings","Number", -c(1,13))
```


Separated columns melted
```{r separated}
s<-separate(g,col = "Number", into=c("Number","Percent"), sep="/")
```

Cleaning again  
change "-" for "0", and remove dot from number  
Change gender as factor
```{r cleaning_again}
s$Number<-gsub("-","0",s$Number)
s$Percent<-gsub("-","0",s$Percent)
s$year<-gsub("\\.","",s$year)
s['gender']<-lapply(s['gender'], factor)
```

**The data is tidy!**
```{r tidy}
head(s,n=20)
```

Now I did examples how is possible compare earnings by gender in two ways.
I limited to the first rows.
Obviously, many other ways are possible to do comparison.

```{r compare1}
s1<-s%>%
 select(-Number)%>%        
 filter(gender!="Both sexes")%>%
 filter(Earnings!="total")%>%
 spread(key=gender,value=Percent)
head(s1,20L)
```

```{r compare2}
s2<-s%>%
 select(-Number)%>%        
 filter(gender!="Both sexes")%>%
 filter(Earnings!="total")%>%
 spread(key=gender,value=Percent)%>%        
 arrange(Earnings,year)
 head(s2,20L)
```
 
The answer the question is better filter by one year range, 35 to 39 years   
in this case male have higher earning than female

```{r compare3}
 s3<-s%>%
         select(-Number)%>%        
         filter(gender!="Both sexes")%>%
         filter(Earnings!="total")%>%
         filter(year=="35_to_39years")%>%
         spread(key=gender,value=Percent)
 head(s3,20L)
```