---
title: "SiqueiraCampos_proj2"
author: "Marco Siqueira Campos"
date: "9 de outubro de 2016"
output: html_document
---


DATA 607  
MSDA CUNY  

PROJECT 2  
ASSIGNMENT WK5     
Tidying and Transforming Data  

github [link](https://github.com/MarcoSCampos/DATA607_proj2)

EXERCISE 2
Religious vs income

Proposal: Marco Siqueira Campos

From: PEW Reserach Center
Source: http://www.pewforum.org/religious-landscape-study/income-distribution/


load library

```{r load_library, warning=FALSE, message=FALSE}
library(tidyr)
library(dplyr)
```

read and check csv file 
```{r read_file}
df_td<-read.table("~/proj2_2.csv",sep=",",stringsAsFactors = FALSE)
df_td
```

Set columns names
```{r columns_names}
colnames(df_td)<-c("Religion","below30k","from30kto49k","from50kto99k","from100k","sample")
```

Cleaning the data

Remove row 1
```{r remove_row}
df_td<-df_td[-1,]
```

Remove "," and "%"
```{r remove_charac}
df_td$sample<-as.numeric(gsub(",","",df_td$sample))
df_td$below30k<- as.numeric(gsub("%","",df_td$below30k))
df_td$from30kto49k<- as.numeric(gsub("%","",df_td$from30kto49k))
df_td$from50kto99k<- as.numeric(gsub("%","",df_td$from50kto99k))
df_td$from100k<- as.numeric(gsub("%","",df_td$from100k))
```

Return the number value
```{r return_number}
for (i in 2:5) {
df_td[,i]<-round((df_td[,i]/100)*df_td[,6])
}
```

Remove column sample
```{r remove_column}
df_td$sample<-NULL
```

Gather the data, move several data column to one column
```{r gather}
df_td2<-gather(df_td,income,count,below30k:from100k)
```

**The data is tidy!**
```{r tidy}
df_td2
```

Is to time to analyse some data, check one religion, Hindu, and we can see a large income.

```{r analy}
df_td3<-df_td2
df_td3%>%
filter(Religion=="Hindu")%>%
       mutate(percent=round(100*count/sum(count)))
```

